%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[hidelinks]{hyperref}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{url}
\usepackage{multicol}
\usepackage[left=2cm, right=2cm, top=1.5cm, bottom = 1.5cm]{geometry}
\usepackage[utf8]{inputenc}
\pagenumbering{arabic}




\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{\Large{\underline{Brato Chakrabarti}}\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Flatiron Institute, Simons Foundation} \\Research Fellow: Center for Computational Biology \\ Biophysical Modeling
\\  162 5$^{\textrm{th}}$ Avenue, NY 10010 \\
\emph{Web:} \url{https://www.bratochakrabarti.com/} } % Your address 1

\address{{\bf Mailing address} \\ 15 East, 11$^{\textrm{th}}$ Street  \\ Apt 4A, NY 10003\\ (540)838-1590} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{{RESEARCH INTEREST}}

\vspace{8pt} % Gap between title and text

\begin{multicols}{3}
    \begin{itemize}
    	\item[] Soft-matter Physics
    	\item[] Fluid-structure Interaction
    	\item[] Scientific Computing
    	\item[] Dynamical Systems
    	\item[] Chaotic Advection
    	\item[] Biophysics
    	\item[] Slender Structures
    	\item[] Complex Fluids
    	\item[] Hydrodynamic Stability
    \end{itemize}
\end{multicols}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{{EDUCATION}} 

\vspace{8pt} % Gap between title and text
{\sl Research Fellow} \\
Center for Computational Biology  \hfill March 2020-Ongoing \\
Flatiron Institute, Simons Foundation  \\
Mentor: Professor Michael J Shelley 

{\sl Doctor of Philosophy}, 
Applied Mechanics \\ 
Department of Mechanical and Aerospace Engineering \hfill Fall 2015-Fall 2019 \\ 
Thesis: Problems on Viscous Dynamics of Passive and Active Microfilaments \\
Advisor: Professor David Saintillan \\
GPA: 4.0/4.0
 
{\sl Master of Science}, Engineering Mechanics \\ 
Biomedical Engineering and Mechanics (BEAM), Virginia Tech \hfill Fall 2013-Spring 2015 \\
Thesis: Catenaries in visocus fluid \\
Advisor: Professor James Hanna \\
GPA: 4.0/4.0

{\sl Bachelor of Engineering}, Mechanical Engineering \\ 
Jadavpur University, India\hfill 2009-2013 \\
GPA: 8.9/10 


%----------------------------------------------------------------------------------------
 


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{{RESEARCH EXPOSURE}} 

\vspace{8pt} % Gap between title and text

{\sl Microscale flow modeling, Saintillan research group} \hfill Fall 2015-ongoing \\
MAE, UC San Diego \hfill Graduate research assisatant
\vspace{2mm}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Bending,buckling and coiling of actin filaments in shear and extensional flow.
\item Spontaneous oscillations of filaments and hydrodynamic synchronization.
\item Shear dispersion in peristaltic flow and bacterial suspension.
\item Mixing, transport and drift due to swimming microorganisms.
\end{itemize}

{\sl Complex suspensions, Anke Lindner Research Group} \hfill Fall 2017-ongoing \\
ESPCI, Paris \hfill Visiting student
\vspace{2mm}
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Dynamics of suspension of flexible filaments.
	\item Buckling and fluctuation dynamics of actin filaments.
\end{itemize}

{\sl Engineering Science and Mechanics, Virginia Tech} \hfill Fall 2013-Spring 2015\\[2pt]
Biomedical Engineering and Mechanics (BEAM) \hfill Graduate research assistant
\vspace*{2mm}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Dynamics and geometry of towed catenaries in viscous fluids. 
\item Geometric phase and chaotic advection in journal bearing flow: relation to swimming microorganisms.
\end{itemize} 
 



%----------------------------------------------------------------------------------------

\section{{PUBLICATIONS} {($^*$ denotes equal contribution)} }
\vspace*{6mm}
\begin{enumerate}
		\item \textbf{Brato Chakabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, ``A multiscale biophysical model gives quantized metachronal waves in a lattice of cilia",  in review, \url{arXiv:2108.01693}, 2021.
		
	\item \textbf{Brato Chakabarti}, Yanan Liu, Olivia du Roure, Anke Lindner, and David Saintillan, ``Signatures of elastoviscous buckling in the dilute rheology of stiff polymers",  \textit{Journal of Fluid Mechanics},  \textbf{919} A12 (2021).
	
	\item \textbf{Brato Chakrabarti}, and David Saintillan, ``Shear-induced dispersion in peristaltic flow", \textit{Physics of Fluids}, \textbf{32} 11302 (2020).  \textbf{Invited:} ``Contributions from Early Career Researchers 2020" and selected as a \textbf{featured} article.
		
	\item \textbf{Brato Chakrabarti}, Charles Gaillard, and David Saintillan, ``Trapping, gliding, vaulting: Transport of semiflexible polymers in periodic post arrays", \textit{Soft Matter}, \textbf{16} 5534 (2020).
		
	
	\item \textbf{Brato Chakrabarti}, Yanan Liu, John Lagrone, Ricardo Cortez, Lisa Fauci, Olivia du Roure, David Saintillan, and Anke Lindner, ``Flexible filaments buckle into helicoidal shapes in strong compressional flow'',  \textit{Nature Physics}, (2020).
	
   \item \textbf{Brato Chakrabarti} and David Saintillan, ``Hydrodynamic synchronization of spontaneously beating filaments'', \textit{Physical Review Letters}, \textbf{123} 208101 (2019). 
 
   
	\item \textbf{Brato Chakrabarti} and David Saintillan, ``Spontaneous oscillations, beating patterns and hydrodynamics of active filaments", \textit{Physical Review Fluids}, \textbf{4} 043102 (2019). 
	
	
	\item Roberto Alonso Matilla, \textbf{Brato Chakrabarti} and David Saintillan, ``Transport and dispersion of active particles in periodic porous media", \textit{Physical Review Fluids}, \textbf{4} 043101 (2019). 
	
	\item Yanan Liu$^*$, \textbf{Brato Chakrabarti}$^*$, David Saintillan, Anke Lindner and Olivia du Roure, ``Tumbling, buckling, snaking: Morphological transitions
	of flexible filaments in shear flow", \textit{Proceedings of the National Academy of Sciences of the USA}, \textbf{115} 9438 (2018).
	
	
	\item \textbf{Brato Chakrabarti} and James Hanna ``Catenaries in Viscous Fluid", \textit{Journal of Fluids and Structure}, \textbf{66} 490–516 (2016).

\end{enumerate}

\vspace*{-0.2cm}

%\subsubsection*{In preperation}
%\begin{enumerate}
%	\item Chenji Li, \textbf{Brato Chakrabarti}, Achal Mahajan, and David Saintillan, ``Hydrodynamics of swimming sperm cells powered by active filaments".
%	
%	\item  \textbf{Brato Chakrabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, ``Phase synchronization in oriented active gels". 
%	
%	\item  \textbf{Brato Chakrabarti}, Sebastian F\"{u}rthauer and Michael J Shelley, ``Continuum theory and phase dynamics of oscillators with steric interactions". 
%		
%  \item Francesco Bonacci, \textbf{Brato Chakrabarti}, David Saintillan, Olivia du Roure, and Anke Lindner ``Dynamics of semiflexible polymers in oscillatory shear flows ".
%\end{enumerate}


\section{{CONFERENCE ARTICLES AND PRESENTATIONS}} 
\vspace*{1mm}
{(Presenter underlined)}
\vspace*{1mm}
\begin{itemize}
		\item \underline{Brato Chakabarti}, Yanan Liu, Olivia du Roure, Anke Lindner, and David Saintillan, \textit{Signatures of elastoviscous buckling in the dilute rheology of stiff polymers}, at the 73rd Annual Meeting of the APS Division of Fluid Dynamics, November 2020 (online).
		
		\item \underline{David Saintillan}, and Brato Chakrabarti, \textit{Hydrodynamic synchronization of spontaneously beating filaments
		}, at the 72nd Annual Meeting of the APS Division of Fluid Dynamics, November 2019, Seattle, USA.
	
		\item \underline{Brato Chakrabarti}, Yanan Liu, John Lagrone, Ricardo Cortez, Lisa Fauci, Olivia du Roure, David Saintillan, and Anke Lindner \textit{Helical buckling of flexible filaments in viscous flow},  at the 72nd Annual Meeting of the APS Division of Fluid Dynamics, November 2019, Seattle, USA.
	
	\item \underline{Anke Lindner}, Brato Chakrabarti, Yanan Liu, Olivia du Roure and David Saintillan, \textit{The dynamics of flexible Brownian fibers in viscous flows} at  The Annual European Rheology Conference, Slovenia, April 8-11, 2019.
	
	\item \underline{Brato Chakrabarti} and David Saintillan, \textit{Spontaneous oscillations and hydrodynamics of active micro-filament} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 
	
	\item Roberto Alonso Matilla, Brato Chakrabarti and \underline{David Saintillan}, \textit{Asymptotic transport and dispersion of active particles in periodic porous media} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 
	
	\item Brato Chakrabarti, \underline{Yanan Liu}, David Saintillan, Anke Lindner and Olivia du Roure, \textit{The dynamics of flexible and Brownian filaments in viscous flows} at the 71st Annual Meeting of the APS Division of Fluid Dynamics, November 2018, Atlanta, USA. 
	
	\item \underline{Brato Chakrabarti}, Yanan Liu, David Saintillan, Anke Lindner and Olivia du Roure, \textit{Buckling and migration of semi-flexible filaments} at the 70th Annual Meeting of the APS Division of Fluid Dynamics, November 2017,
	Denver,USA. 
	
	\item \underline{David Saintillan} and Brato Chakrabarti, \textit{Shear dispersion in peristaltic pumping} at the 70th Annual Meeting of the APS Division of Fluid Dynamics, November 2017,
		Denver,USA. 
	
	\item \underline{James Hanna} and Brato Chakrabarti, \textit{Catenaries in viscous fluid}. $24^{th}$ ICTAM, Montreal, August 2016.
	
	\item \underline{Brato Chakrabarti} and David Saintillan. \textit{Drift, Mixing and Diffusivity in 
		Stokes Flow}. Presented at the Southern California (SoCal) Fluids X, April 2016, UC Irvine, California, USA.
	
	\item Brato Chakrabarti and \underline{James Hanna}. \textit{Catenaries in viscous fluid}. At the 68th Annual Meeting of the APS Division of Fluid Dynamics, November 2015,
	Boston, USA. 
	
	\item \underline{Brato Chakrabarti} and James Hanna. \textit{Catenaries in Drag}. Presented at the 67th Annual Meeting of the APS Division of Fluid Dynamics, November 2014,
	San Francisco, USA. 
	
	%\item  \underline{Arindam Bit}, Brato Chakrabarti and Himadri Chattopadhyay. \textit{Haemodynamics in Stenosed Artery}. Proceedings of Indian Science Congress, Kolkata, January 2013.
	
	%\item \underline{Brato Chakrabarti} and Himadri Chattopadhyay. \textit{Optimization of the Bronchial Tree Using Constructal Theory}. Proceedings of International Conference on Advances in Mechanical Engineering and its Interdisciplinary Areas', held at CEM, Kolaghat, West Bengal, India in December 2012. Pg: 384-392 (ISBN: 978-93-82062-79-0) 
\end{itemize}

\vspace*{-0.15cm}
\section{{AWARDS AND HONORS}}
\vspace*{6mm}
	\begin{itemize}
		\item \textbf{Powell Fellow, UCSD} by Jacobs school of Engineering, Fall 2015
		
		
		\item \textbf{Pratt Presidential Graduate Fellowship} by Virginia Tech to the incoming outstanding graduate students, 2013-2014.
		
		\item \textbf{Awarded Gold Medal} for best performance in Fluid Mechanics in Bachelor of Engineering (Mechanical Engineering, Jadavpur University), 2013.
		
		\item \textbf{Awarded a Summer Research Fellowship} by the Indian Academy of Sciences for undertaking a research project during May--July 2012.
		
     	\item \textbf{National Merit Scholarship} for outstanding performance in school leaving examination, 2009.
		\end{itemize}

\section{{REVIEWER FOR ARCHIVED JOURNALS}}
\vspace*{8mm}
\begin{multicols}{2}
\begin{itemize}
	\item Journal of Fluid Mechanics
	\item Physical Review Fluids
	\item Journal of Mathematical Fluid Mechanics
	\item Physical Review E
	\item Physical Review Letters
	\item Soft Matter
\end{itemize}
\end{multicols}
		

\section{{COMPUTER SKILLS}}

\vspace*{8mm}
\begin{itemize}
	\item \textbf{Programming skills:} Fortran 90/95, Python
	\item \textbf{Scientific software:} Matlab, Mathematica, Simulink
	\item \textbf{Documentation/graphics:} \LaTeX, Beamer, Igor-Pro, Adobe illustrator
\end{itemize}



\section{{TEACHING EXPERIENCE}}
\paragraph{At Virginia Tech} 
\begin{itemize}
	\vspace*{2mm}
	\item Fall 2013: Teaching Assistant, Statics  (ESM 2104)
	\item Spring 2014: Teaching Assistant, Dynamics (ESM 2204)
	\item Fall 2014: Teaching Assistant, Anaytical mechanics (ESM 3214)
	\item Spring 2015: Teaching Assistant, Vibrations (ESM 3134)
\end{itemize}

\paragraph{At UCSD} 
\begin{itemize}
    \vspace*{2mm}
	\item Winter 2017: Teaching Assistant, Fluid mechanics (MAE 210 A)
	\item Fall   2018: Teaching Assistant, Introduction to mathematical physics (MAE 105).
	\item Spring 2019: Teaching Assistant, Hydrodynamic stability (MAE 210 C)
\end{itemize}
%----------------------------------------------------------------------------------------

\vspace*{0.1 in}

%----------------------------------------------------------------------------------------

%\section{{INTERESTS}} 

%\vspace*{8mm}


%\begin{itemize}
%	\item Playing Sarode (an Indian string instrument) and tabla (an Indian %percussion).
%	\item Indian classical and folk music.
%	\item Science education and outreach.
%\end{itemize}

\section{\centerline{REFERENCES}} 

\vspace*{6mm}

\begin{enumerate}		
	\item Prof. David Saintillan\\
	Professor\\
	Department of Mechanical and Aerospace Engineering, UCSD\\
	E-mail: dsaintillan@eng.ucsd.edu  \hspace{3mm} Web: \url{http://stokeslet.ucsd.edu/} \\
	
			\item Prof. Michael Shelley\\
	Lilian and George Lyttle Professor of Applied Mathematics\\
	The Courant Institute of Mathematical Sciences   	 \vspace*{0.5mm} 	 \\
	Director, Center for Computational Biology \\ 
	The Flatiron Institute, Simons Foundation\\
	E-mail: mshelley@simonsfoundation.org  \hspace{3mm} Web: \url{https://math.nyu.edu/faculty/shelley/} \\
	
	\item Prof. Anke Lindner \\
	Professor \\
	Department of Physics, University Paris Diderot \\
	E-mail: anke.lindner@espci.fr   \hspace{3mm} Web: \url{https://blog.espci.fr/alindner/} \\
	
		\item Prof. Stefan Llewellyn Smith\\
	Professor\\
	Department of Mechanical and Aerospace Engineering, UCSD\\
	E-mail: sllewellynsmith@ucsd.edu \hspace{3mm} Web: \url{https://sites.google.com/a/eng.ucsd.edu/sgls/} \\
	
	
	\item Prof. James Hanna\\
	Associate Professor\\
	Department of Mechanical Engineering,	University of Nevada, Reno\\
	E-mail: jhanna@unr.edu \hspace{3mm} Web: \url{https://cmag.neocities.org/index.html} \\
	

   
\end{enumerate}
%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}